\documentclass[letterpaper,11pt]{article}

\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{authblk} % authors and affiliations
\usepackage{parcolumns} % questions and answers in columns

\input{definitions}
\newcommand\amelia[0]{\textsc{Amelia}}
\newcommand\ie[0]{\textit{i.e.}}
\newcommand{\question}[1]{\colchunk{\begin{description}[style=unboxed,leftmargin=0cm]\item{#1}\end{description}}}
\newcommand{\answer}[1]{\colchunk{\begin{description}[style=unboxed,leftmargin=0cm]\item{#1}\end{description}}\colplacechunks}

\title{\textbf{Amelia Evaluation}\\User Questionnaire}

\author[1]{Miguel Jim\'{e}nez}
\author[2]{Luis F. Rivera}
\author[2]{Norha M. Villegas}
\author[2]{Gabriel Tamura}
\author[1]{Hausi A. M\"{u}ller}
\affil[1]{University of Victoria, Victoria, Canada}
\affil[2]{Universidad Icesi, Cali, Colombia}
\date{}
\setcounter{Maxaffil}{0}
\renewcommand\Affilfont{\itshape\small}

\begin{document}
\maketitle

\Qitem{Please indicate the time you spent (in minutes) specifying the deployment: \Qline{1.5cm}}

\Qitem{Please describe the difficulties you experienced developing the deployment assets. \Qlines{3}}

\Qitem{How much time have you been working as a professional Software Engineer? \Qline{1.5cm}}

\Qitem{Please describe how much experience you have deploying software. \Qlines{3}}

\Qitem{Please describe how much experience you have with the \amelia{} DSL. \Qlines{3}}

\noindent
Please indicate your agreement or disagreement with the following statements by selecting only one square. The left-most square indicates that you \textbf{strongly agree}, while the right-most square indicates that you \textbf{strongly disagree}.

\paragraph{Functional Suitability}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{In the software deployment domain, all concepts and building-blocks to solve the addressed problem can be expressed in \amelia{}.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} is an appropriate and useful tool for deploying software.}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Usability}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{The language elements are understandable (\textit{e.g.}, language elements can be understood after reading their descriptions).}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{The concepts and symbols of the language resemble the terminology of the deployment domain, are learnable and rememberable (\ie{}, learning easiness, easiness for developing deployment specifications).}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} helps users achieve their deployment tasks in acceptable development times.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} is appropriate for the deployment of the type of software you work on.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} has useful language elements to control the actual deployment operations (\textit{e.g.}, language elements can be selected and put into practice easily, actions are undoable, error messages that explain recovery methods are available for controlling the deployment operations).}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} has a concise syntax that allows expressing deployment operations in short specification files.}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Reliability}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{\amelia{} prevents making errors in deployment specifications. The language constructs helps the user to avoid mistakes.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} includes the right elements and correct relationships between them (it prevents unexpected interactions between its elements).}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Maintainability}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{\amelia{} is composed of discrete components such that a change to one component has minimal impact on other components.}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Productivity}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{The development time of writing software deployment specifications is improved.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} allows to compose and reuse language elements, which increase efficiency at writing deployment specifications. }}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} helps to improve the productivity of system deployment.}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Expressiveness}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{A deployment strategy can be mapped into a \amelia{} specification easily.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} provides one and only one good way to express every concept of interest.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{Each \amelia{} construct is used to represent exactly one distinct concept in the application domain.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{The language constructs correspond to significant application domain concepts. \amelia{} does not include domain concepts that are not important.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} does not contain conflicting or ambiguous elements.}}
	\answer{\Qrating{5}}
	\colplacechunks
	
	\question{\Qitem{\amelia{} is at the right abstraction level for writing deployment specifications, such that it is not more complex or more detailed than necessary.}}
	\answer{\Qrating{5}}
	\colplacechunks
\end{parcolumns}

\paragraph{Integrability}
\begin{parcolumns}[colwidths={1=0.76\textwidth},nofirstindent]{2}
	\question{\Qitem{\amelia{} can be integrated with other languages used in the software development process, such as using already developed libraries. (\textit{e.g.}, language integrability with other languages).}}
	\answer{\Qrating{5}}
	\colplacechunks
	
\end{parcolumns}
	
\end{document}
